---
title: "District Dungeons"
output: html_document
date: "2023-11-25"
version: 1.0
---


Install packages as needed:

```{r echo=FALSE message=FALSE}
install.packages("tidyverse")
install.packages("sf")
install.packages("ggpubr")
install.packages("png")
install.packages("jpeg")
install.packages("ggpattern")
install.packages("magick")
install.packages("jsonlite")
```


```{r echo=FALSE message=FALSE}
library(tidyverse)
library(sf)
library(ggpubr)
library(png)
library(jpeg)
library(ggpattern)
library(magick)
library(jsonlite)
```


The script starts by checking for all available district geometries and then eliminates duplicates, removing all but the most recent version of the district.

```{r}
a <- data.frame(url=character())

directories <- fromJSON("https://api.github.com/repositories/15808774/contents/cds")[["url"]]

for (dir in directories) {
  b <- fromJSON(dir)["url"]
  a <- rbind(a, b)
}

district <- a[["url"]] %>% str_split_i("/", -1) %>% str_split_i("[?]", 1)
year <- a[["url"]] %>% str_split_i("/", -2)
jsonURL <- paste("https://theunitedstates.io/districts/cds", year, district, "shape.geojson", sep="/")

a["year"] <- year
a["district"] <- district
a["jsonURL"] <- jsonURL

districts <- a %>% group_by(district) %>% filter(year==max(year)) %>% ungroup() %>% select("jsonURL", "district")

#districts
```


By default, this script saves images for all 400+ district geometries available from <https://theunitedstates.io> as .png images with a resolution of 320 ppi. To adjust the image resolution, change the `dpi` argument of the `ggsave` function. Valid values for dpi include numbers and the strings "retina" (320), "print" (300), and "screen" (72).

```{r}
for (dist in districts[["jsonURL"]]) {

  names <- districts %>% filter(jsonURL==dist)
  name <- names[["district"]]
  filename <- paste(name, ".png", sep="")

  map <- read_sf(dist)
  background <- readJPEG("images/dirt.jpg")
  tiles <- "images/tiles.png"

  ggplot(map) +
    background_image(background) +
    geom_sf_pattern(
      aes(),
      pattern          = 'image',
      pattern_filename = tiles,
      pattern_type     = 'tile',
      pattern_scale=.75
    ) +
    theme(
      axis.text.x=element_blank(), #remove x axis labels
      axis.ticks.x=element_blank(), #remove x axis ticks
      axis.text.y=element_blank(),  #remove y axis labels
      axis.ticks.y=element_blank()  #remove y axis ticks
    )

  ggsave(filename, path="output", dpi="retina")
}
```
